Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-04-14 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
updating manuscript based on comments by Ferreira

\subsection{Order parameters from experiments}\label{expORDp}
The order parameter of a hydrocarbon C--H vector is defined as 
\begin{equation}\label{orderP}
S_{{\rm CH}}=\frac{1}{2}\langle 3 \cos^2 \theta-1 \rangle,
\end{equation} 
where the angle brackets denote an ensemble average over the sampled conformations, and $\theta$ is the angle between the C--H bond and the membrane normal.
The absolute values of order parameters can be measured by detecting quadrupolar splitting with $^2$H NMR~\cite{seelig77c} or by detecting dipolar 
splitting with $^{13}$C NMR~\cite{hong95a,gross97,dvinskikh05a,ferreira13}. The measurements are based on
different physical interactions and also the connection between order parameters and quadrupolar or dipolar splitting
are different. The absolute values of order parameters from the measured quadrupolar splitting $\Delta \nu_Q$ ($^2$H NMR) are calculated using 
the equation $|S_{{\rm CD}}|=\frac{4}{3} \frac{e^2qQ}{h} \Delta \nu_Q$, where the value for the static quadrupole
splitting constant is estimated from various experiments to be 170~kHz leading to a numerical relation $|S_{{\rm CD}}|=0.00784 \times \Delta \nu_Q$~\cite{seelig77c}. 
The absolute values of order parameters from the measured dipolar splitting $d_\mathrm{CH}$ ($^{13}$C NMR) are calculated using equation
$|S_{{\rm CH}}|=\frac{4\pi\langle r_\mathrm{CH}^3 \rangle}{\hbar \mu_0 \gamma_h \gamma_c} d_\mathrm{CH}$, where
values between 20.2--22.7 kHz are used for $\frac{4\pi\langle r_\mathrm{CH}^3 \rangle}{\hbar \mu_0 \gamma_h \gamma_c}$,
depending on the original authors~\cite{hong95a,gross97,dvinskikh05a,ferreira13}.
It is important to note that the order parameters measured with different techniques based on different physical interactions are in good agreement
with each other (see Results and Discussion), indicating very high quantitative accuracy of the measurements.
For a more detailed discussion see \url{http://nmrlipids.blogspot.fi/2014/02/accuracy-of-order-parameter-measurements.html}
\todo{Citation to the blog will be added when available.}

The absolute values of order parameters are accessible with both $^2$H NMR and $^{13}$C NMR techniques. 
However, only $^{13}$C NMR techniques allow also the measurement of the sign of the order parameter~\cite{hong95a,hong95b,gross97}. 
The measured sign is negative for almost all the carbons discussed in this work as only $\alpha$ is positive~\cite{hong95a,hong95b,gross97}. 
For more detailed discussion about the sign measurements of the order parameters see \url{http://nmrlipids.blogspot.fi/2014/04/on-signs-of-order-parameters.html}
\todo{Citation to the blog will be added when available.}

For most CH$_2$ segments in fluid phosholipid bilayer the order parameters are equal for both hydrogens attached to the same carbon.
However, in some cases (e.g. g$_1$, g$_3$ and  C$_2$ carbon in the \textit{sn}-2 chain) the order parameters are not equal and this 
can be observed with both $^2$H NMR and $^{13}$C NMR techniques. In the present work we call the phenomena of unequal order parameters 
for hydrogens attached to the same carbon as {\it forking} to avoid confusion with dipolar and quadrupolar splitting in NMR terminology. 
Forking has been studied in detail with $^2$H NMR techniques by deuterating the R or S position in CH$_2$ segment, and
the studies show that the forking arises from differently sampled orientations of the two C--H bonds, not from two 
separate populations of lipid conformations~\cite{engel81,gally81}.

@@

\subsection{Full hydration: Experimental order parameters for the glycerol backbone and headgroup}\label{experiments}
The specific deuteration of $\alpha$-, $\beta$- and g$_3$- segments of DPPC has been successful, 
allowing the absolute value order parameter measurements for these segments by $^2$H--NMR~\cite{gally75,brown77,brown78,akutsu81}.
In addition, the absolute values of order parameters for all glycerol backbone and choline headgroup segments in egg yolk lecithin~\cite{hong95a},
DMPC~\cite{hong95b,gross97,dvinskikh05a}, DOPC~\cite{warschawski05} and POPC~\cite{warschawski05,ferreira13}
have been measured with several different implementations of $^{13}$C NMR experiments. In addition, the signs of order parameters in some systems
are measured with $^{13}$C NMR techniques~\cite{hong95a,hong95b,gross97}. The experimental values of glycerol backbone 
and choline order parameters from various publications~\cite{gally75,akutsu81,gross97,dvinskikh05a,ferreira13} with the signs measured in~\cite{hong95a,hong95b,gross97} are shown in Fig.~\ref{HGorderparameters}.
\begin{figure}[]
%  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/comparisonSorted.pdf}
%\todo{Markus Miettinen suggested that we should consider making one more figure where only experimental data would be shown and that would be discussed in Section~\ref{experiments}. \\
%COMMENT: I do not think that we need such figure anymore since this figure is more clear now.} \\
\newline
\todo{There is also the interactive version by Hubert Santuz now in https://plot.ly/~HubertSantuz/72/lipid-force-field-comparison/
we should figure out which is the most practical way to put that behind permalink once it finalized (Zenodo, figshare or something else?) and then put a citation in the paper.}
  \caption{\label{HGorderparameters}
  Order parameteres from simulations listed in Table~\ref{systems} and experiments for glycerol and choline groups.
The experimental values were taken from the following publications:
 DMPC 303~K from \cite{gross97},
 DMPC 314~K from \cite{dvinskikh05a},
 DPPC 322~K from \cite{gally75},
 DPPC 323~K from \cite{akutsu81},
 POPC 296~K from \cite{bechinger91}, and
 POPC 300~K from \cite{ferreira13}.
  The vertical bars shown for some of the computational values are not error bars, but demonstrate that for 
these systems we had at least two data sets (see Table~\ref{systems});
the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average. 
} 
\end{figure}

In general there is a good agreement between the order parameters measured with different experimental NMR techniques: Almost all the 
reported values are within a variation of $\pm$0.02 (which is also the error estimate given by Gross et al.~\cite{gross97}) 
for all fully hydrated PC bilayer, regardless of the variation in their acyl chain composition and temperature.
Exceptions are the somewhat lower order parameters sometimes reported from measurements using $^{13}$C--NMR~\cite{hong95a,hong95b,warschawski05}.
These experiments are not shown in Fig.~\ref{HGorderparameters} as the reported error bars are either relatively large~\cite{hong95a,hong95b}, 
or the spectral resolution is quite low and the numerical lineshape simulations have not been used in the analysis~\cite{warschawski05}.
Due to this end, it is highly likely that these reported lower order parameters are due to lower experimental 
accuracy and therefore we exclude them from our discussion. 
For more details, see \url{http://nmrlipids.blogspot.fi/2014/02/accuracy-of-order-parameter-measurements.html}
\todo{Citation to the blog will be added when available.}
Motivated by the high experimental repeatability, we have highlighted in 
Fig.~\ref{HGorderparameters} the subjective sweet spots (light blue areas), within which we expect the calculated absolute 
values of the order parameters of a well-performing force field to fall.

@@

\subsection{Response to dehydration and cholesterol content}
In addition to pure phosphatidylcholine bilayers at full hydration, the choline headgroup order parameters
have been measured under various different conditions~\cite{gally75,brown77,brown78,akutsu81,altenbach84,scherer89,bechinger91,ulrich94,dvinskikh05b,castro08,kapla12,ferreira13}.
Also the order parameters for the glycerol backbone have been measured with $^{13}$C NMR in dehydrated conditions~\cite{dvinskikh05b}, and as a function 
of anesthetics~\cite{castro08} and glycolipids~\cite{kapla12} for DMPC, and as a function of cholesterol 
concentration for POPC~\cite{ferreira13}. Due to the high resolution in the NMR (especially $^2$H NMR) experiments,
even very small order parameter changes resulting from the varying conditions can be measured (see
\url{http://nmrlipids.blogspot.fi/2014/02/accuracy-of-order-parameter-measurements.html}
for more discussion.)
\todo{Citation to the blog will be added when available.}
However, as already discussed above, it is not simple to deduce 
the structural changes from order parameter changes~\cite{akutsu91,semchyschyn04}. Consequently, comparison of the order parameters
between simulations and experiments in different conditions can be used to assess the quality of the force field 
in different situations, and, if the quality is good, to potentially interpret the structural changes in experiments.
Here we exemplify such comparison for a lipid bilayer under low hydration levels and when varying amounts of cholesterol is included in the bilayer. 
The interaction between ions and a phosphatidylcholine bilayer will be discussed in a separate study~\cite{ionpaper}.

\subsubsection{Phospholipid bilayer with low hydration level}
The experimental order parameters available in the literature~\cite{dvinskikh05b,ulrich94,bechinger91} 
for the glycerol backbone and choline as a function of hydration level are shown in Fig.~\ref{ordPhydr}. 
The independently reported values for choline segments are in good agreement with each other (despite 
slight differences in temperature and acyl chain composition),
showing increase for both segments with decreasing hydration level. It should be noted that only 
absolute values were measured in the original experiments~\cite{dvinskikh05b,ulrich94,bechinger91}, but
we have included the signs measured in separate studies~\cite{hong95a,hong95b,gross97}. 
Consequently, the $\beta$ order parameter with negative sign actually increases with dehydration 
since the absolute value decreases~\cite{dvinskikh05b,ulrich94,bechinger91}.
Slight decrease for the glycerol backbone order parameters were observed with dehydration~\cite{dvinskikh05b}.
\begin{figure}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/dehydration.pdf} \\
  \todo{DONE} \\
  \caption{\label{ordPhydr}
    The effect of dehydration on glycerol and choline order parameters in experiments.
    The magnitudes of order parameters are measured for DMPC ($^{13}$C NMR) at 314~K~\cite{dvinskikh05b}, 
    for POPC ($^2$H NMR) at 296~K~\cite{bechinger91} and for DOPC ($^2$H NMR) at 303~K~\cite{ulrich94}. 
    The signs are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
    and Gross et al.~\cite{gross97}.
    Note that to elucidate the relative change as a function of hydration level,
    the simulation results are shifted such that the (smaller) $S_\mathrm{CH}$
    matches (within $\pm$0.01) the experimental value at full hydration;
    the shift magnitudes for each of the force fields are listed ($S_\mathrm{CH}$+shift) in the y-label.
  }
\end{figure}

@@

The choline headgroup and glycerol backbone order parameters for POPC measured by $^{13}$C NMR~\cite{ferreira13} and DPPC choline order parameters 
measured by $^{2}$H NMR~\cite{brown78} are shown in Fig.~\ref{ordPchol} as a function of cholesterol content.
The agreement between different experimental results is again very good, showing only very modest changes in 
the choline order parameters as a function of cholesterol content. It should be noted, however, that very small
changes are measurable with high resolution $^{2}$H NMR experiments
and cholesterol causes a measurable increase in the $\beta$ order parameter and a forking in the $\alpha$ order
parameter~\cite{brown78}. These effects are, however, so small that they are barely visible in the scale used in Fig.~\ref{ordPchol}.
Further, the effects of cholesterol on the glycerol backbone order parameters for POPC from $^{13}$C NMR experiment~\cite{ferreira13} 
are in good agreement with the results for the phosphatidylethanolamine (PE) measured by $^{2}$H NMR~\cite{ghosh82}.
These results further support the idea that the glycerol backbone structural behaviour is independent of the
headgroup composition~\cite{gally81} and that the headgroup stucture is independent of the acyl chain region content unless
charges are present~\cite{scherer87}.
\begin{figure}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/cholesterolization.pdf} \\
  \todo{DONE} \\
  \caption{\label{ordPchol}
    The effect of cholesterol content on the glycerol backbone and choline order parameters in experiments~\cite{brown78,ferreira13} and simulations
    with the Berger-POPC-07/H\"oltje-CHOL-13, CHARMM36 and MacRog force fields. The signs in the experimental values are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
    and Gross et al.~\cite{gross97}.  Most order parameters from Berger-POPC-07/H\"oltje-CHOL-13 model for g$_1$ are beoynd the y-axis scale.
    Note that to elucidate the relative change as a function of cholesterol content,
    the simulation results are shifted such that the (smaller) $S_\mathrm{CH}$
    matches (within $\pm$0.01) the experimental value without cholesterol;
    the shift magnitudes for each of the force fields are listed ($S_\mathrm{CH}$+shift) in the y-label.
}
\end{figure}

>>>>

\subsection{Order parameters from experiments}\label{expORDp}
The order parameter of a hydrocarbon C--H vector is defined as 
\begin{equation}\label{orderP}
S_{{\rm CH}}=\frac{1}{2}\langle 3 \cos^2 \theta-1 \rangle,
\end{equation} 
where the angle brackets denote an ensemble average over the sampled conformations, and $\theta$ is the angle between the C--H bond and the membrane normal.
The absolute values of order parameters can be measured by detecting quadrupolar splitting with $^2$H NMR~\cite{seelig77c} or by detecting dipolar 
splitting with $^1$H-$^{13}$C NMR~\cite{hong95a,gross97,dvinskikh05a,ferreira13}. The measurements are based on
different physical interactions and also the connection between order parameters and quadrupolar or dipolar splitting
are different. The absolute values of order parameters from the measured quadrupolar splitting $\Delta \nu_Q$ ($^2$H NMR) are calculated using 
the equation $|S_{{\rm CD}}|=\frac{4}{3} \frac{e^2qQ}{h} \Delta \nu_Q$, where the value for the static quadrupole
splitting constant is estimated from various experiments to be 170~kHz leading to a numerical relation $|S_{{\rm CD}}|=0.00784 \times \Delta \nu_Q$~\cite{seelig77c}. 
The absolute values of order parameters from the effective dipolar coupling $d_\mathrm{CH}$ ($^1$H-$^{13}$C NMR) are calculated using equation
$|S_{{\rm CH}}|=\frac{4\pi\langle r_\mathrm{CH}^3 \rangle}{\hbar \mu_0 \gamma_h \gamma_c} d_\mathrm{CH}$, where
values between 20.2--22.7 kHz are used for $\frac{4\pi\langle r_\mathrm{CH}^3 \rangle}{\hbar \mu_0 \gamma_h \gamma_c}$,
depending on the original authors~\cite{hong95a,gross97,dvinskikh05a,ferreira13}.
The effective dipolar coupling $d_\mathrm{CH}$ is related to the measured dipolar splitting $\Delta \nu_{CH}$ 
through scaling factor which depends on the pulse sequence used in the $^1$H-$^{13}$C NMR experiment~\cite{hong95a,gross97,dvinskikh05a,ferreira13}.
It is important to note that the order parameters measured with different techniques based on different physical interactions are in good agreement
with each other (see Results and Discussion), indicating very high quantitative accuracy of the measurements.
For a more detailed discussion see \url{http://nmrlipids.blogspot.fi/2014/02/accuracy-of-order-parameter-measurements.html}
\todo{Citation to the blog will be added when available.}

The absolute values of order parameters are accessible with both $^2$H NMR and $^1$H-$^{13}$C NMR techniques. 
However, only $^1$H-$^{13}$C NMR techniques allow also the measurement of the sign of the order parameter~\cite{hong95a,hong95b,gross97}. 
The measured sign is negative for almost all the carbons discussed in this work as only $\alpha$ is positive~\cite{hong95a,hong95b,gross97}. 
For more detailed discussion about the sign measurements of the order parameters see \url{http://nmrlipids.blogspot.fi/2014/04/on-signs-of-order-parameters.html}
\todo{Citation to the blog will be added when available.}

For most CH$_2$ segments in fluid phosholipid bilayer the order parameters are equal for both hydrogens attached to the same carbon.
However, in some cases (e.g. g$_1$, g$_3$ and  C$_2$ carbon in the \textit{sn}-2 chain) the order parameters are not equal and this 
can be observed with both $^2$H NMR and $^1$H-$^{13}$C NMR techniques. In the present work we call the phenomena of unequal order parameters 
for hydrogens attached to the same carbon as {\it forking} to avoid confusion with dipolar and quadrupolar splitting in NMR terminology. 
Forking has been studied in detail with $^2$H NMR techniques by deuterating the R or S position in CH$_2$ segment, and
the studies show that the forking arises from differently sampled orientations of the two C--H bonds, not from two 
separate populations of lipid conformations~\cite{engel81,gally81}.

@@

\subsection{Full hydration: Experimental order parameters for the glycerol backbone and headgroup}\label{experiments}
The specific deuteration of $\alpha$-, $\beta$- and g$_3$- segments of DPPC has been successful, 
allowing the absolute value order parameter measurements for these segments by $^2$H NMR~\cite{gally75,brown77,brown78,akutsu81}.
In addition, the absolute values of order parameters for all glycerol backbone and choline headgroup segments in egg yolk lecithin~\cite{hong95a},
DMPC~\cite{hong95b,gross97,dvinskikh05a}, DOPC~\cite{warschawski05} and POPC~\cite{warschawski05,ferreira13}
have been measured with several different implementations of $^1$H-$^{13}$C NMR experiments. In addition, the signs of order parameters in some systems
are measured with $^1$H-$^{13}$C NMR techniques~\cite{hong95a,hong95b,gross97}. The experimental values of glycerol backbone 
and choline order parameters from various publications~\cite{gally75,akutsu81,gross97,dvinskikh05a,ferreira13} with the signs measured in~\cite{hong95a,hong95b,gross97} are shown in Fig.~\ref{HGorderparameters}.
\begin{figure}[]
%  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/comparisonSorted.pdf}
%\todo{Markus Miettinen suggested that we should consider making one more figure where only experimental data would be shown and that would be discussed in Section~\ref{experiments}. \\
%COMMENT: I do not think that we need such figure anymore since this figure is more clear now.} \\
\newline
\todo{There is also the interactive version by Hubert Santuz now in https://plot.ly/~HubertSantuz/72/lipid-force-field-comparison/
we should figure out which is the most practical way to put that behind permalink once it finalized (Zenodo, figshare or something else?) and then put a citation in the paper.}
  \caption{\label{HGorderparameters}
  Order parameteres from simulations listed in Table~\ref{systems} and experiments for glycerol and choline groups.
The experimental values were taken from the following publications:
 DMPC 303~K from \cite{gross97},
 DMPC 314~K from \cite{dvinskikh05a},
 DPPC 322~K from \cite{gally75},
 DPPC 323~K from \cite{akutsu81},
 POPC 296~K from \cite{bechinger91}, and
 POPC 300~K from \cite{ferreira13}.
  The vertical bars shown for some of the computational values are not error bars, but demonstrate that for 
these systems we had at least two data sets (see Table~\ref{systems});
the ends of the bars mark the extreme values from the sets, and the dot marks their measurement-time-weighted average. 
} 
\end{figure}

In general there is a good agreement between the order parameters measured with different experimental NMR techniques: Almost all the 
reported values are within a variation of $\pm$0.02 (which is also the error estimate given by Gross et al.~\cite{gross97}) 
for all fully hydrated PC bilayer, regardless of the variation in their acyl chain composition and temperature.
Exceptions are the somewhat lower order parameters sometimes reported from measurements using $^1$H-$^{13}$C NMR~\cite{hong95a,hong95b,warschawski05}.
These experiments are not shown in Fig.~\ref{HGorderparameters} as the reported error bars are either relatively large~\cite{hong95a,hong95b}, 
or the spectral resolution is quite low and the numerical lineshape simulations have not been used in the analysis~\cite{warschawski05}.
Due to this end, it is highly likely that these reported lower order parameters are due to lower experimental 
accuracy and therefore we exclude them from our discussion. 
For more details, see \url{http://nmrlipids.blogspot.fi/2014/02/accuracy-of-order-parameter-measurements.html}
\todo{Citation to the blog will be added when available.}
Motivated by the high experimental repeatability, we have highlighted in 
Fig.~\ref{HGorderparameters} the subjective sweet spots (light blue areas), within which we expect the calculated absolute 
values of the order parameters of a well-performing force field to fall.

@@

\subsection{Response to dehydration and cholesterol content}
In addition to pure phosphatidylcholine bilayers at full hydration, the choline headgroup order parameters
have been measured under various different conditions~\cite{gally75,brown77,brown78,akutsu81,altenbach84,scherer89,bechinger91,ulrich94,dvinskikh05b,castro08,kapla12,ferreira13}.
Also the order parameters for the glycerol backbone have been measured with $^1$H-$^{13}$C NMR in dehydrated conditions~\cite{dvinskikh05b}, and as a function 
of anesthetics~\cite{castro08} and glycolipids~\cite{kapla12} for DMPC, and as a function of cholesterol 
concentration for POPC~\cite{ferreira13}. Due to the high resolution in the NMR (especially $^2$H NMR) experiments,
even very small order parameter changes resulting from the varying conditions can be measured (see
\url{http://nmrlipids.blogspot.fi/2014/02/accuracy-of-order-parameter-measurements.html}
for more discussion.)
\todo{Citation to the blog will be added when available.}
However, as already discussed above, it is not simple to deduce 
the structural changes from order parameter changes~\cite{akutsu91,semchyschyn04}. Consequently, comparison of the order parameters
between simulations and experiments in different conditions can be used to assess the quality of the force field 
in different situations, and, if the quality is good, to potentially interpret the structural changes in experiments.
Here we exemplify such comparison for a lipid bilayer under low hydration levels and when varying amounts of cholesterol is included in the bilayer. 
The interaction between ions and a phosphatidylcholine bilayer will be discussed in a separate study~\cite{ionpaper}.

\subsubsection{Phospholipid bilayer with low hydration level}
The experimental order parameters available in the literature~\cite{dvinskikh05b,ulrich94,bechinger91} 
for the glycerol backbone and choline as a function of hydration level are shown in Fig.~\ref{ordPhydr}. 
The independently reported values for choline segments are in good agreement with each other (despite 
slight differences in temperature and acyl chain composition),
showing increase for both segments with decreasing hydration level. It should be noted that only 
absolute values were measured in the original experiments~\cite{dvinskikh05b,ulrich94,bechinger91}, but
we have included the signs measured in separate studies~\cite{hong95a,hong95b,gross97}. 
Consequently, the $\beta$ order parameter with negative sign actually increases with dehydration 
since the absolute value decreases~\cite{dvinskikh05b,ulrich94,bechinger91}.
Slight decrease for the glycerol backbone order parameters were observed with dehydration~\cite{dvinskikh05b}.
\begin{figure}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/dehydration.pdf} \\
  \todo{DONE} \\
  \caption{\label{ordPhydr}
    The effect of dehydration on glycerol and choline order parameters in experiments.
    The magnitudes of order parameters are measured for DMPC ($^1$H-$^{13}$C NMR) at 314~K~\cite{dvinskikh05b}, 
    for POPC ($^2$H NMR) at 296~K~\cite{bechinger91} and for DOPC ($^2$H NMR) at 303~K~\cite{ulrich94}. 
    The signs are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
    and Gross et al.~\cite{gross97}.
    Note that to elucidate the relative change as a function of hydration level,
    the simulation results are shifted such that the (smaller) $S_\mathrm{CH}$
    matches (within $\pm$0.01) the experimental value at full hydration;
    the shift magnitudes for each of the force fields are listed ($S_\mathrm{CH}$+shift) in the y-label.
  }
\end{figure}

@@

The choline headgroup and glycerol backbone order parameters for POPC measured by $^1$H-$^{13}$C NMR~\cite{ferreira13} and DPPC choline order parameters 
measured by $^{2}$H NMR~\cite{brown78} are shown in Fig.~\ref{ordPchol} as a function of cholesterol content.
The agreement between different experimental results is again very good, showing only very modest changes in 
the choline order parameters as a function of cholesterol content. It should be noted, however, that very small
changes are measurable with high resolution $^{2}$H NMR experiments
and cholesterol causes a measurable increase in the $\beta$ order parameter and a forking in the $\alpha$ order
parameter~\cite{brown78}. These effects are, however, so small that they are barely visible in the scale used in Fig.~\ref{ordPchol}.
Further, the effects of cholesterol on the glycerol backbone order parameters for POPC from $^1$H-$^{13}$C NMR experiment~\cite{ferreira13} 
are in good agreement with the results for the phosphatidylethanolamine (PE) measured by $^{2}$H NMR~\cite{ghosh82}.
These results further support the idea that the glycerol backbone structural behaviour is independent of the
headgroup composition~\cite{gally81} and that the headgroup stucture is independent of the acyl chain region content unless
charges are present~\cite{scherer87}.
\begin{figure}[]
  \centering
  \includegraphics[width=8.6cm]{../DATAreportediINblog/cholesterolization.pdf} \\
  \todo{DONE} \\
  \caption{\label{ordPchol}
    The effect of cholesterol content on the glycerol backbone and choline order parameters in experiments~\cite{brown78,ferreira13} and simulations
    with the Berger-POPC-07/H\"oltje-CHOL-13, CHARMM36 and MacRog force fields. The signs in the experimental values are based on the measurements by Hong et al.~\cite{hong95a,hong95b} 
    and Gross et al.~\cite{gross97}.  Most order parameters from Berger-POPC-07/H\"oltje-CHOL-13 model for g$_1$ are beoynd the y-axis scale.
    Note that to elucidate the relative change as a function of cholesterol content,
    the simulation results are shifted such that the (smaller) $S_\mathrm{CH}$
    matches (within $\pm$0.01) the experimental value without cholesterol;
    the shift magnitudes for each of the force fields are listed ($S_\mathrm{CH}$+shift) in the y-label.
}
\end{figure}
